
\chapter{Related Works}\label{ch:related}

Our purpose is to construct a automated web testing tool and evaluation method.
Web testing and test evaluation have been studied many years since 2001\cite{WebTesting}.
We survey the similar tools\cite{WebToolsList}  and researchs about testing web applications and test oracles.
They are shown as the following.

%本篇測試的目標是web 和 Android APP，列出常見的testing 工具

\section{Web testing}

Testing tool likes Jmeter\cite{jmeter} record the script of uset behavior and reply it on the web pages.
Jmeter is not focus on functional testing but on load testing.
It creates many threads to test the specific websites simultaneously or reply the test lots of times.
It measure the performance of the web applications and the servers.

Selenium\cite{selenium} is a tool which can also record test scripts with friendly interface on firefox.
Except for recording, selenium also can assertions in the test cases.
Selenium is a powerful library for web testing.
User can write their test scripts on most of language likes C\#, Python, Ruby, Java and Perl.

TestStudio\cite{Teststudio} and TestComplete\cite{Smartbear} is platform which has frienfdly GUI interface for user.
It can record scripts and implement functional testing and performane testing.
During testing, it captures not only snapshots but also informations of objects.
User can also write their own plugin to control the test scripts.

VeriWeb is tool presented by Benedikt et al.\cite{veriweb}
for automatically exploring dynamic websites and execution paths including form submissions and client-side script.
To testing websites used Ajax, which is based on asynchronous communication with server,
Marchetto et al.\cite{Search-BasedTesting} proposed state-based testing and construct a finite state machines to explore websites.

Crawljax\cite{crawljax} presented by Mesbath et al. is a java open source tool 
which can automated explore dynamic websites and 
collect the invariants of the Document Object Model of the web pages to construct finite state machine.
It records traces by Depth-first search algorithm and generates state flow graph.
User can write own API to control test scripts or add assertions.

%selenium,jmeter 需要先建立testcase 再重複測試
%VeriWeb，CrawlJax可自動explore website,建立DOM tree，用DOM建state-based testing

\section{Test evaluation}
	
In software testing, testers use an oracle as a mechanism for determining whether a test has passed or failed
in order to reduce human cost.
The test oracle should capture the properties of the system to find test cases and counter examples.
Assertions may be used to check the specified behaviors of systems at runtime.
Barr et al.\cite{OracleProblem} gathererd the oracle problem in software testing into four categories.

Kanewala et al.\cite{DetectMetamorphic} seek to find the metamorphic relations, 
which focus on the relations between different executions of the applications and inferred from white box inspection of the SUT,
using machine learning techniques.
Derived test oracle distinguishes between the correct and incorrect behaviors of the SUT based on the properties pd th system.
Daikon is a tool, which is presented bt Ernst et al.\cite{SupportProgramEvolution}, 
to find likely invariants from traces automatically.


%test oracle use on software testing, finite state machine
%metamorphic relations, 
